EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-07 draft.tex
Introduction to the General Exp Setup
@jj  please check
Addresses @mariosky query about experimental setup

We aimed to learn if the proposed solution can efficiently
improve the scalability and performance of population-based optimization
algorithms. Hence, in the following sections, we verify the following:

\begin{itemize}
\item Whether we can improve the execution time of the algorithm by adding populations
 and serverless functions to the system, in particular, what is the effect of
 these changes on the scalability of the system?

\item Having a multi-population enabled platform, with heterogeneous populations and
the support for mixing search strategies,  increases the performance of the
search by needing fewer function evaluations than a homogeneous setting?
\end{itemize}

To validate these questions, we used benchmark functions from the Continuous
Noiseless BBOB testbed, which is part of the Comparing Continuous Optimizers
(COCO) framework \cite{hansen2016coco}. The testbed includes 24 real-parameter,
single-objective benchmark functions, and the capability to provide additional
instances of each function. Each instance of a function has a different optimal
value. The standard benchmark of the testbed utilizes 15 instances per function
over 2, 3, 5, 10, 20, and 40 dimensions. The maximum number of Function
Evaluations (FEs) changes according to the dimension (D), and it is determined
by the expression $10^5 \cdot D$. As an example, if we have $D = 2$, the
maximum number of FEs is $200,000$

@@

% This is only an idea of the section
%
% First you have to say that cloud is a way of describing deployment to any kind of infrastructure in a reproducible way, and it needn't be in the cloud proper, it can be deployed to anything, that's precisely the thing. But make clear that when you use a cloud provider, there are more options to do it... - JJ
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation. % Remember that Salza et al. used CoreOS, which is optimized for containers - JJ

>>>>

We aimed to learn if the proposed solution can efficiently
improve the scalability and performance of population-based optimization
algorithms. % If you want to prove it *improves*, you need to provide a baseline. What will be your baseline? You need to specify anyway in which way it really improves - JJ
Hence, in the following sections, we verify the following:

% JJ these are the three experiments, please check them. The last two addressing
% issues from a reviewer - M

\begin{itemize}
\item Can we improve the execution time of the algorithm by adding populations
 and serverless functions to the system and, in particular, what is its effect on the scalability of the system?

\item Does having a multi-population enabled platform, with heterogeneous populations and
the support for mixing search strategies,  increases the performance of the
search by needing fewer function evaluations than a homogeneous setting? % But in this case the answer is no, right? - JJ

\item Can EvoSwarm as a cloud-native, container-based application,  be deployed
locally or in the cloud by just specifying the configuration of container images
and resources to an orchestration service?
\end{itemize}

To validate these questions, we used benchmark functions from the Continuous
Noiseless BBOB testbed, which is part of the Comparing Continuous Optimizers
(COCO) framework \cite{hansen2016coco}. The testbed includes 24 real-parameter,
single-objective benchmark functions, and the capability to provide additional
instances of each function. Each instance of a function has a different optimal
value. The standard benchmark of the testbed utilizes 15 instances per function
over 2, 3, 5, 10, 20, and 40 dimensions. The maximum number of Function
Evaluations (FEs) changes according to the dimension (D), and it is determined
by the expression $10^5 \cdot D$. As an example, if we have $D = 2$, the
maximum number of FEs is $200,000$.
% How do you manage to stop exactly at that number of evaluations in a distributed system? - JJ

@@

% This is only an idea of the section
%
% First you have to say that cloud is a way of describing deployment to any kind of infrastructure in a reproducible way, and it needn't be in the cloud proper, it can be deployed to anything, that's precisely the thing. But make clear that when you use a cloud provider, there are more options to do it... - JJ
% You should start writing this out soon... Don't leave it this way - JJ
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation. % Remember that Salza et al. used CoreOS, which is optimized for containers - JJ
